---
title: "p8105_hw1_js5165"
author: "Jingqi Song"
date: "September 20, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

##Problem 1
```{r problem1}
set.seed(0920)
p1_df = tibble(
  x = runif(10, min = 0, max = 5),
  vec_logical = x > 2,
  vec_char = c("one", "two", "three", "four","five","six","seven","eight","nine","ten"),
  vec_factor = factor(c("male", "male", "female", "female","male", "male", "female", "female","male", "female"))
)
p1_df

mean(p1_df$x)
mean(p1_df$vec_logical)
mean(p1_df$vec_char)
mean(p1_df$vec_factor)
```
I can get the mean of numeric and logical variables, but not characer or factor ones.

###Problem 1 Convert 1 
```{r problem1_convert1, result = 'hide'}

as.numeric(p1_df$vec_logical)
as.numeric(p1_df$vec_char)
as.numeric(p1_df$vec_factor)
```

Logical and factor variables can be converted to numeric variables, but character variable can be converted.

###Problem 1 Convert 2 
```{r problem1_convert2}
as.numeric(as.factor(p1_df$vec_char))
as.numeric(as.character(p1_df$vec_factor))
```

The character variable can be finally converted to numeric variable; but the logical variable cannot be converted to numeric variable if first converted to character variable.

##Problem 2 
```{r problem2}
set.seed(0921)
p2_df = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  vec_logical = x + y > 0，
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical)
)
p2_df

```







